Global search algorithm with local tuning for solving mixed-integer global optimization problems \thanks{This study was supported by the .}

### 2021-02-15 2021/MOTOR_BarkalovLebedev/MOTOR2021.tex
1. Таблица 4 дополнена

\begin{table}[ht]
\centering
\caption{The results of a series of experiments to solve bi-criteria five-dimensional MOO problems}
\label{tab:4}
\begin{tabular}{cccclccclccc}
\hline
\multirow{3}{*}{\begin{tabular}[c]{@{}c@{}}Number of \\ functions in\\ $\Phi_p (y)$\end{tabular}} & \multicolumn{11}{c}{Algorithms}                                                     \\ \cline{2-12} 
                                                                                        & \multicolumn{3}{c}{GSA} &  & \multicolumn{3}{c}{MGSA} &  & \multicolumn{3}{c}{SGSA} \\
                                                                                        & Iters   & HV    & DU    &  & Iters   & HV     & DU    &  & Iters   & HV     & DU    \\ \hline
25                                                                                      & 1030039.6 & 2.440 & 0.543 & & 619755.6 & 2.441 & 0.681 & & 669743.8 & 2.364 & 0.668 \\ \hline
\end{tabular}
\end{table}

The results of our experiments show that with increasing dimensionality of the MOO problems to be solved, the trend that has been identified continues: the amount of computation (the number of global search iterations) is reduced by more than 1.6 times due to reuse of search information, the MGSA algorithm performs the least number of iterations, and the SGSA algorithm provides the best approximation of the Pareto domain.

>>>>

\begin{table}[ht]
\centering
\caption{The results of a series of experiments to solve bi-criteria five-dimensional MOO problems}
\label{tab:4}
\begin{tabular}{cccclccclccc}
\hline
\multirow{3}{*}{\begin{tabular}[c]{@{}c@{}}Number of \\ functions in\\ $\Phi_p (y)$\end{tabular}} & \multicolumn{11}{c}{Algorithms}                                                     \\ \cline{2-12} 
                                                                                        & \multicolumn{3}{c}{GSA} &  & \multicolumn{3}{c}{MGSA} &  & \multicolumn{3}{c}{SGSA} \\
                                                                                        & Iters   & HV    & DU    &  & Iters   & HV     & DU    &  & Iters   & HV     & DU    \\ \hline
25                                                                                      & 1030039.6 & 2.440 & 0.543 & & 619755.6 & 2.441 & 0.681 & & 669743.8 & 2.364 & 0.668 \\ 
50                                                                                      & 2061634.2 & 2.502 & 0.572 & & 647508.2 & 2.533 & 0.691 & & 710418.6 & 2.417 & 0.680 \\ 
100                                                                                     & 4104694.4 & 2.504 & 0.686 & & 683410.5 & 2.555 & 0.696 & & 728485.3 & 2.483 & 0.696 \\ \hline
\end{tabular}
\end{table}

The results of our experiments show that with increasing dimensionality of the MOO problems to be solved, the trend that has been identified continues: the amount of computation (the number of global search iterations) is reduced by more than 5.6 times due to reuse of search information, the MGSA algorithm performs the least number of iterations, and the SGSA algorithm provides the best approximation of the Pareto domain.
